---
title: "R Notebook"
output: html_notebook
---

```{r}
library(psych)
```

```{r}
data <- read.csv('data.csv')
```


```{r}
#View(data)
```

```{r}
data$HG_NHG<-as.factor(data$HG_NHG)
data$HG_NHG2<-as.factor(data$HG_NHG2)
```

```{r}
data$Status1<-as.factor(data$Status1)
```

```{r}
summary(data)
```

 
```{r}
library(dplyr)
data %>% count(Status1, HG_NHG)
  
```

```{r}
library(ggplot2)
data %>%
  group_by(Status1) %>%
  ggplot(aes(value, color=Status1)) + 
  geom_histogram(aes(fill = Status1), bins = 20) +
  facet_wrap(~Status1) +
  theme_grey()+
  labs(x= "Anzahl der Perceptions of corruption",y = "Anzahl" )
```


```{r}
data %>%
  group_by(HG_NHG) %>%
  ggplot(aes(value, color=HG_NHG)) + 
  geom_histogram(aes(fill = HG_NHG), bins = 20) +
  facet_wrap(~HG_NHG) +
  theme_grey()+
  labs(x= "Anzahl der Perceptions of corruption",y = "Anzahl" )
```

```{r}
ggplot(data, aes(x=value))+
geom_histogram(bins = 25)+
theme_grey()+
facet_wrap(Status1~HG_NHG, ncol = 2)
```



```{r}
ggplot(data, aes(Status1, value, fill=factor(HG_NHG))) +
geom_boxplot() +
theme_minimal()+
labs(fill = "Income Level", x="Status", y="Anzahl Score")
```


```{r}
ggplot(data, aes(x=HG_NHG, y=value, group=Status1, color = Status1))+
  stat_summary(fun.y = mean, geom="point", size=3)+
  stat_summary(fun.y = mean, geom="line")+
  stat_summary(fun.data = mean_cl_normal, geom="errorbar",width=.2, size=.25)+
  labs(x="Income Level", y="Corruption")+
  theme_classic()

```

```{r}
library(car)
```


```{r}
leveneTest(value ~ Status1*HG_NHG, data = data, center = "mean")

```

Mit Welch-Korrektur: p < 0.05 => Ergebnis Signifikant –> Varianzen heterogen

Ohne Welch-Korrektur: p > 0.05 => Ergebnis nicht Signifikant –> Varianzen homogen –> H0 mit Annahme Var1=Var2=… -> Var_n wird angenommen

```{r}

```


```{r}

multiAnova1 <- lm(value ~ Status1*HG_NHG, data = data)
myAnova <- Anova(multiAnova1 , type = 3)
myAnova
```

```{r}
Statuswelch <- oneway.test(value ~ Status1, data = data, var.equal = F)
Statuswelch
```

```{r}
Incomewelch <- oneway.test(value ~ HG_NHG, data = data, var.equal = F)
Incomewelch
```

```{r}
Mixwelch <- oneway.test(value ~ HG_NHG*Status1, data = data, var.equal = F)
Mixwelch
```

```{r}
PostHoc <- aov(value ~ Status1*HG_NHG, data=data) 
#Alternativ auch der Name des Zwischenspeichers "mehr" - PostHoc <- aov(mehr)  
TukeyHSD(PostHoc)
```

```{r}
library(rstatix)
data['merge'] <- paste(data$Status1,data$HG_NHG)

gm <- rbind(games_howell_test(data, value ~ Status1),games_howell_test(data, value ~ HG_NHG),games_howell_test(data, value ~ merge))
gm
```


```{r}
library(sjstats)
```

```{r}
eta <- effectsize::eta_squared(multiAnova1, partial = TRUE)
```

```{r}
eta
```


```{r}
st <- sqrt(0.47/(1-0.47))

sprintf("effectsize for Freedom Status: f= %.3f", st)
```

```{r}
st <- sqrt(0.19/(1-0.19))
sprintf("effectsize for Income Level: f= %.3f", st)
```

```{r}
st <- sqrt(0.03/(1-0.03))
sprintf("effectsize for Income Level X Freedom Status: f= %.3f", st)
```

According to result there is a relation between Freedom Hause index und  Corruption  (F(1, 111.85) = 98.595, p = 2.2e-16). H1 is accepted. Moreover for Income Level there are also differences  between Income level Corruption (F(1,140.36) = 89.419, p <  2.2e-16). H1 is accepted. The Interaction effects of  Income Level und Freedom Hause index  Corruption is significant (F(3,58.136) = 56.567, p < 2.2e-16). The effect of Income Leve is dependent on partially Freedom Hause index. H1  for interaction is accepted.

Regarding the Posthoc test, the impact of Freedom and income level is clear, but their interaction should be analyzed carefully. for instance, the differences between non-democratic countrıes with high-income levels and democratic countries with low-income levels are not significant. 

Die effect size ist not only for Freedom Hause index (f = 0.942) but also for income Level (f = 0.484) according to Cohen (1988) a strong effekt, and for interaction (f=0.176) is middle. 
 

 
 
 
 
 
